### 2015-03-19 supp/supp.tex
modification of the table of mutation signature nuns…

>>>>

\begin{table}
\caption{The number of mutation signatures selected for each cancer type.
}
\begin{center}
\begin{tabular}{|c|c|} \hline
cancer type & \# mutation signature \\ \hline
AML & 2 \\ \hline
ALL & 3 \\ \hline
Bladder & 3 \\ \hline
Breast & 4 \\ \hline
Cervix & 3 \\ \hline
CLL & 3 \\ \hline
Colorectum & 5 \\ \hline
Esophageal & 4 \\ \hline
Glioblastoma & 3 \\ \hline
Glioma-Low-Grade & 3 \\ \hline
Head-and-Neck & 5 \\ \hline
Kidney-Chromophobe & 3 \\ \hline
Kidney-Clear-Cell & 3 \\ \hline
Kidney-Papillary & 3 \\ \hline
Liver & 3 \\ \hline
Lung-Adeno & 4 \\ \hline
Lung-Small-Cell & 4 \\ \hline
Lung-Squamous & 3 \\ \hline
Lymphoma-B-Cell & 4 \\ \hline
Medulloblastoma & 3 \\ \hline
Melanoma & 4 \\ \hline
Myeloma & 3 \\ \hline
Neuroblastoma & 3 \\ \hline
Ovary & 3 \\ \hline
Pancreas & 4 \\ \hline
Pilocytic-Astrocytoma & 4 \\ \hline
Prostate & 2 \\ \hline
Stomach & 5 \\ \hline
Thyroid & 4 \\ \hline
Uterus & 4 \\ \hline
\end{tabular}
\end{center}
\label{tab_rep}
\end{table}
